\documentclass[margin,line]{res}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\usepackage{hyperref}

\begin{document}

\name{Simon Xiang \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
    University of Texas at Austin & {\it E-mail:}  \href{mailto:simonxiang@utexas.edu}{\texttt{simonxiang@utexas.edu}}\\       
    Austin, TX 78712-1082 & {\it Website:} \url{www.simonxiang.xyz}
\end{tabular}


\section{\sc About}
Freshman mathematics major at UT Austin with a focus in pure math, aspiring to go to graduate school for mathematics. U.\! S.\! Citizen. 

\section{\sc Education}
{\bf University of Texas at Austin}, Austin, Texas USA\\
\vspace*{-.1in}
\begin{list1}
\item[] B.S., Mathematics, expected May 2024 
\end{list1}

{\bf Texas Academy of Mathematics and Science}, Denton, Texas USA\\
\vspace*{-.1in}
\begin{list1}
\item[] TAMS, May 2020
\end{list1}

\section{\sc Academic Experience}
{\bf University of Texas at Austin}, Austin, Texas USA

\vspace{-.3cm}
{\em Undergraduate Student} \hfill {\bf August 2020 - present}\\

\vspace{-.3cm}
\begin{list2}
\item Took a graduate algebraic topology course as a freshman. Currently enrolled in graduate differential topology and Riemannian geometry.
\item Undergraduate courses taken include differential geometry (current), complex analysis, and differential equations. More information on coursework can be found here: \url{www.simonxiang.xyz/math}
\item Active participant in the math club.
\item Currently studying de Rham cohomology and characteristic classes in DRP (Directed Reading Program), a program where you study a specific topic in depth, mentored by a graduate student.
\end{list2}


{\bf University of North Texas}, Denton, Texas USA

\vspace{-.3cm}
{\em TAMS Student} \hfill {\bf August 2018  - May 2020}\\
Completed 62 credit hours of coursework in residence at UNT. Relevant courses taken include:
\vspace{0.1cm}
\begin{list2}
\item Calculus 2, Multivariable Calculus, Linear Algebra (2018-2019)
\item Real Analysis, Discrete Math (self-study, Summer 2019)
\item Abstract Algebra, Real Analysis II (Fall 2019)
\item Topology, Abstract Algebra II (Spring 2020)
\end{list2}

\vspace{-.3cm}
Qualified for the NAQT quiz bowl national championship (HSNCT) in both Spring 2019 and 2020.

{\em Math Tutor} \hfill {\bf August 2019  - May 2020}\\
Volunteered several hours peer week to tutor fellow TAMS students in higher level math courses, including multivariable calculus, linear algebra, and real analysis.

\section{\sc Computer Skills} 
\begin{list2}
\item Languages:  \LaTeX{}, HTML and CSS, Unix shell scripts. Familiar with C and C++.
\item Operating Systems:  Arch Linux (home system), Ubuntu/Debian (server).
\item System administration: Currently hosting a git server, mail server, and personal website on a VPS running Debian 10.
\item \LaTeX{}: Live-\TeX{}es notes in Vim for math classes and hosts them on personal website.
\item Linux: Set up home system on Arch Linux with dwm, running mostly terminal based programs, all free and open source. 
\end{list2}

\section{\sc Personal Hobbies} 
\begin{list2}
\item Ran the Galveston marathon in Februrary 2020, aiming to complete a triathlon in 2021.
\item Semi-fluent in Japanese (self-study, estimated B2 proficiency) and  Chinese (spoken at home).
\item Created a minimal personal website (\url{www.simonxiang.xyz}) with a blog on various topics.
%\item Modified my window manager and terminal emulator, all other personal projects (including my website and math notes) can be viewed here: \url{git.simonxiang.xyz}
\end{list2}


\end{resume}
\end{document}
